Simulations (mix normal prior), ctwas_rss, 45k samples

### 2021-04-09 analysis/simulation-ctwas-ukbWG-gtex.adipose_s40.22.Rmd
fusion plot fix bug

    f1 <- caliFUSIONp_plot(phenofs, fusioncolocfs)
    f2 <- ncausalFUSIONp_plot(phenofs, fusioncolocfs)
    f3 <- caliPP4_plot(phenofs, fusioncolocfs)
    f4 <- ncausalPP4_plot(phenofs, fusioncolocfs)
    gridExtra::grid.arrange(f1, f2, ncol=2)
    gridExtra::grid.arrange(f3, f4, ncol=2)
}
```

>>>>

    f1 <- caliFUSIONp_plot(phenofs, fusioncolocfs)
    f2 <- ncausalFUSIONp_plot(phenofs, fusioncolocfs)
    f3 <- caliPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    f4 <- ncausalPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    gridExtra::grid.arrange(f1, f2, ncol=2)
    gridExtra::grid.arrange(f3, f4, ncol=2)
}
```

### 2021-04-09 analysis/simulation-ctwas-ukbWG-gtex.adipose_s40.22_mixnormal.Rmd
fusion plot fix bug

    f1 <- caliFUSIONp_plot(phenofs, fusioncolocfs)
    f2 <- ncausalFUSIONp_plot(phenofs, fusioncolocfs)
    f3 <- caliPP4_plot(phenofs, fusioncolocfs)
    f4 <- ncausalPP4_plot(phenofs, fusioncolocfs)
    gridExtra::grid.arrange(f1, f2, ncol=2)
    gridExtra::grid.arrange(f3, f4, ncol=2)
}
```

```{r param, fig.height=3, fig.width=8, message=F}

>>>>

    f1 <- caliFUSIONp_plot(phenofs, fusioncolocfs)
    f2 <- ncausalFUSIONp_plot(phenofs, fusioncolocfs)
    f3 <- caliPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    f4 <- ncausalPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    gridExtra::grid.arrange(f1, f2, ncol=2)
    gridExtra::grid.arrange(f3, f4, ncol=2)
}
```

```{r param, fig.height=3, fig.width=10, message=F}

### 2021-04-09 analysis/simulation-ctwas-ukbWG-gtex.adipose_s80.45_mixnormal.Rmd
fusion plot fix bug

    f1 <- caliFUSIONp_plot(phenofs, fusioncolocfs)
    f2 <- ncausalFUSIONp_plot(phenofs, fusioncolocfs)
    f3 <- caliPP4_plot(phenofs, fusioncolocfs)
    f4 <- ncausalPP4_plot(phenofs, fusioncolocfs)
    gridExtra::grid.arrange(f1, f2, ncol=2)
    gridExtra::grid.arrange(f3, f4, ncol=2)
}
```

```{r param2, fig.height=3, fig.width=8, message=F}

>>>>

    f1 <- caliFUSIONp_plot(phenofs, fusioncolocfs)
    f2 <- ncausalFUSIONp_plot(phenofs, fusioncolocfs)
    f3 <- caliPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    f4 <- ncausalPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    gridExtra::grid.arrange(f1, f2, ncol=2)
    gridExtra::grid.arrange(f3, f4, ncol=2)
}
```

```{r param2, fig.height=3, fig.width=10, message=F}
